---
format: 
  html:
    toc: true
    toc-depth: 5
prefer-html: true
title: "Summary"
---

```{r, echo = FALSE, message = FALSE}
library(tidyverse)

data <- read.csv("2022_annualreportdata.csv")

year <- unique(data$Year)

``` 


## `r year` Field Work {.unnumbered}

In 2022, field observers completed 1,348 of 1,415 (95.2%) planned surveys throughout all or portions of BCRs 9, 10, 11, 15, 16, 17, 18, 19, 33, and 34 using the IMBCR design (
<a href="#sec-planned-completed">Table&nbsp;<span>1</span></a>, @fig-extent). Five surveys were completed above the funded sample effort in two strata. Reasons surveys were not completed are summarized in <a href="#sec-reasons">Table&nbsp;<span>2</span></a>. 

Observers conducted 15,137 point counts within the 1,348 surveyed sampling units between May 1 and July 25, 2022. They detected 176,954 individual birds representing 350 species.

Please note that not every stratum or superstratum is summarized in this report. We include details of specific strata or superstrata for which our partners are most interested. However, results from all strata and all biologically meaningful superstrata can be found on the [Rocky Mountain Avian Data Center](http://rmbo.org/v3/avian/ExploretheData.aspx) (RMADC). This online database contains species counts, density, abundance, and occupancy results per strata, and also interactive maps showing approximate survey and detection locations. Instructions for using the RMADC are included in Appendix A of this report and are available on the RMADC website (hover over the “Explore the Data” tab for tutorials). Each stratum or superstratum presented in the Results section contains a web link that leads directly to the RMADC with the appropriate queries already populated.  

Unless otherwise specified, all bird species names listed in this report are from the 63rd supplement to the American Ornithological Society's Check-list of North American Birds (Chesser et al., 2022).


## Trend Estimates {.unnumbered}

We estimated species population trends for data collected through `r year`. Results can be found in [this Google Drive folder](https://drive.google.com/drive/folders/1-ges-7CkLaHHk-BCtNV-SEvIyoqIHhxm?usp=share_link). Please see the associated Read Me document for an explanation of columns in the trend estimates spreadsheet. If you cannot access Google Drive, please contact [Jennifer Timmer](mailto: jennifer.timmer@birdconservancy.org) for a copy of the data.

We do not include trend estimates for species with zero detections in a given stratum. Please use caution when interpreting trends for low-density species at the superstratum (regional) level when there were zero detections in a given year. In these cases, we add a very small number to the estimate (i.e., half the minimum non-zero estimate) in order to take the log of the estimate. This increases uncertainty around the trend estimates.  


## Number of Species with Estimates {.unnumbered}

The way we present density and occupancy estimates in the final report has changed from years prior to 2018. In the past, if a species had been detected in a stratum in a previous year, but was not detected in the current year, we did not provide density or occupancy estimates for that species in that stratum. We now include estimates for these species. In these cases, the estimate for a given year is zero or very close to zero. We consider these to be legitimate estimates of zero occupancy or density because the species occurs in the area of interest, but was not detected in a particular year.  

This change means that the number of species with density or occupancy estimates for a given stratum or superstratum in a given year is not comparable to the number of species with estimates for that stratum or superstratum and year in reports prior to 2018. The number of species in the current report will include species with zero, or near zero estimates, if that species has been detected in previous years, whereas reports before 2018 will not. Therefore, there may be more species with estimates for a given stratum in a final report for 2018 and later. 


## Planned and Completed Strata {.unnumbered}

### Table 1. Planned and completed surveys by strata, 2022. {#sec-planned-completed}

```{r planned-completed, results = "asis", echo = F, message = F}
#| column: screen-inset-right

library(DT)

plan.comp.strata <- read.csv("planned-completed-strata-2022.csv")

plan.comp.strata$percent <- plan.comp.strata$Completed/plan.comp.strata$Planned

plan.comp.strata <- plan.comp.strata %>%
  select(State, bcr, Stratum, LongStratum, Partner, Planned, Completed, percent, Area)


datatable(plan.comp.strata, 
          extensions = 'Buttons',
          options = list(pageLength = 10,
                         autoWidth = FALSE,
                         dom = 'lftpB',
                         buttons = c('copy', 'csv', 'excel'), 
                         columnDefs = list(list(className = 'dt-left', 
                                                targets = c(0,2:3)), 
                                           list(className = 'dt-center', 
                                                targets = c(1, 4:8)))),
          rownames = FALSE,
         # caption = "Table x. Planned and completed surveys by stratum, 2022.",
          colnames = c("State", "BCR", "Stratum", "Stratum Description", 
                       "Who Collected", "Planned", "Completed",
                       "% Completed", "Area (km2)")) %>%
  formatStyle(1:9, fontSize = '12px') %>%
  formatPercentage(8)

# cat("<table>",paste0("<caption style='text-align:right'>", "#tab-planned-completed", "Planned and completed surveys by stratum, 2022.", "</caption>"),"</table>", sep ="\n")


```

:::{.column-screen-inset-right}
BCR = Bird Conservancy of the Rockies; DoD = Department of Defense; GBBO = Great Basin Bird Observatory; IBO = Intermountain Bird Observatory; KBO = Klamath Bird Observatory; UDWR = Utah Division of Wildlife Resources; WYNDD = Wyoming Natural Diversity Database.
:::

<br>
<br>
<br>
    


### Table 2. Reasons planned surveys were not completed, 2022. {#sec-reasons}
```{r, echo = F, message = F}
reasons <- read.csv("reasons-surveys-not-completed.csv")

datatable(reasons, 
          options = list(pageLength = 10,
                         autoWidth = FALSE,
                         dom = 'tip',
                         columnDefs = list(list(className = 'dt-left', 
                                                targets = c(0,2)), 
                                           list(className = 'dt-center', 
                                                targets = 1))),
          rownames = FALSE,
          colnames = c("Stratum", "Number not completed", "Reason")) %>%
          # caption = "Table x. Reasons surveys not completed, 2022.") %>%
  formatStyle(0:2, fontSize = '12px')


```



