---
format: 
  html:
    toc: true
    toc-depth: 4
---
# U.S. Forest Service

```{r echo = FALSE, message = FALSE}

library(tidyverse)
library(xfun) # numbers_to_words function
library(lubridate)

data <- read.csv("2022_annualreportdata.csv")

  data$FirstVisit <- as_date(data$FirstVisit)
  data$FirstVisit <- paste(month(data[,"FirstVisit"], 
                           label = TRUE, abbr = FALSE), 
                           day(data[,"FirstVisit"]), 
                           sep = " ")
  data$LastVisit <- as_date(data$LastVisit)
  data$LastVisit <- paste(month(data[,"LastVisit"], 
                          label = TRUE, abbr = FALSE), 
                          day(data[,"LastVisit"]), 
                          sep = " ")

```

## Region 1

### Region 1 National Forests

```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "USFS-Region 1 National Forests")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[USFS-Region 1 National Forests](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "Beaverhead-Deerlodge National Forest")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[Beaverhead-Deerlodge National Forest](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "Bitterroot National Forest")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[Bitterroot National Forest](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "Clearwater National Forest")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[Clearwater National Forest](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "Custer National Forest")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[Custer National Forest](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "Flathead National Forest")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[Flathead National Forest](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "Gallatin National Forest")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[Gallatin National Forest](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "Helena National Forest")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[Helena National Forest](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "Idaho Panhandle National Forest")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[Idaho Panhandle National Forest](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "Kootenai National Forest")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[Kootenai National Forest](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "Lewis and Clark National Forest")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[Lewis and Clark National Forest](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "Lolo National Forest")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[Lolo National Forest](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "Nez Perce National Forest")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[Nez Perce National Forest](`r hyperlink`)

### Region 1 National Grasslands

```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "USFS-Region 1 National Grasslands")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[USFS-Region 1 National Grasslands](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "ND-BCR17-MG")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[ND-BCR17-MG](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "ND-BCR17-RG")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[ND-BCR17-RG](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "SD-BCR17-RG")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[SD-BCR17-RG](`r hyperlink`)

## Region 2

### Region 2 National Forests

```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "USFS-Region 2 National Forests")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[USFS-Region 2 National Forests](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "CO-BCR16-AR")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[CO-BCR16-AR](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "WY-BCR10-BI")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[WY-BCR10-BI](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "Black Hills National Forest")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[Black Hills National Forest](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "CO-BCR16-GM")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[CO-BCR16-GM](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "Medicine Bow National Forest")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[Medicine Bow National Forest](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "Nebraska National Forests")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[Nebraska National Forests](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "CO-BCR16-PS")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[CO-BCR16-PS](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "Rio Grande National Forest")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[Rio Grande National Forest](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "Routt National Forest")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[Routt National Forest](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "CO-BCR16-SA")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[CO-BCR16-SA](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "Shoshone National Forest")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[Shoshone National Forest](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "White River National Forest")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[White River National Forest](`r hyperlink`)

### Region 2 National Grasslands

```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "USFS-Region 2 National Grasslands")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[USFS-Region 2 National Grasslands](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "Nebraska National Grasslands")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[Nebraska National Grasslands](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "KS-BCR18-CM")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[KS-BCR18-CM](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "CO-BCR18-CO")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[CO-BCR18-CO](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "CO-BCR18-PG")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[CO-BCR18-PG](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "WY-BCR17-TB")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[WY-BCR17-TB](`r hyperlink`)

## Region 3

### Region 3 National Forests

```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "AZ-BCR34-CF")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[Coconino National Forest](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "Coronado National Forest")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[Coronado National Forest](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "Kaibab National Forest")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[Kaibab National Forest](`r hyperlink`)

## Region 4

### Region 4 National Forests

```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "USFS-Region 4 National Forests")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[USFS-Region 4 National Forests](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "Ashley National Forest")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[Ashley National Forest](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "Boise National Forest")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[Boise National Forest](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "Bridger-Teton National Forest")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[Bridger-Teton National Forest](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "Caribou-Targhee National Forest")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[Caribou-Targhee National Forest](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "Dixie National Forest")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[Dixie National Forest](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "Fishlake National Forest")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[Fishlake National Forest](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "Humboldt-Toiyabe National Forest")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[Humboldt-Toiyabe National Forest](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "Manti-La Sal National Forest")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[Manti-La Sal National Forest](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "ID-BCR10-PA")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[ID-BCR10-PA](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "Salmon-Challis National Forest")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[Salmon-Challis National Forest](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "Sawtooth National Forest")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[Sawtooth National Forest](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "Uinta-Wasatch-Cache National Forest")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[Uinta-Wasatch-Cache National Forest](`r hyperlink`)

### Region 4 National Grasslands

```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "ID-BCR9-CU")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[ID-BCR9-CU](`r hyperlink`)

