---
format: 
  html:
    toc: true
    toc-depth: 4
---

# Bureau of Land Management
```{r echo = FALSE, message = FALSE}

library(tidyverse)
library(xfun) # numbers_to_words function
library(lubridate)

data <- read.csv("2022_annualreportdata.csv")

  data$FirstVisit <- as_date(data$FirstVisit)
  data$FirstVisit <- paste(month(data[,"FirstVisit"], 
                           label = TRUE, abbr = FALSE), 
                           day(data[,"FirstVisit"]), 
                           sep = " ")
  data$LastVisit <- as_date(data$LastVisit)
  data$LastVisit <- paste(month(data[,"LastVisit"], 
                          label = TRUE, abbr = FALSE), 
                          day(data[,"LastVisit"]), 
                          sep = " ")

```

## BLM California

### BLM in California BCR 9
```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "CA-BCR9 BLM")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[CA-BCR9 BLM](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "CA-BCR9-CC")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[CA-BCR9-CC](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "CA-BCR9-CD")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[CA-BCR9-CD](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "CA-BCR9-CN")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[CA-BCR9-CN](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "CA-BCR9-NC")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[CA-BCR9-NC](`r hyperlink`)

## BLM Colorado

### BLM in Colorado
```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "CO-BLM")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[CO-BLM](`r hyperlink`)

### BLM in Colorado BCR 10
```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "CO-BCR10-BL")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[CO-BCR10-BL](`r hyperlink`)

### BLM in Colorado BCR 9
```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "CO-BCR16-BL")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[CO-BCR16-BL](`r hyperlink`)

## BLM Idaho

```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "ID-BCR9-BR")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[ID-BCR9-BR](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "ID-BCR9-BU")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[ID-BCR9-BU](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "ID-BCR9-OW")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[ID-BCR9-OW](`r hyperlink`)

## BLM Montana

```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "MT-BLM")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[MT-BLM](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "MT-BCR10-BLM")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[MT-BCR10-BLM](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "MT-BCR11-BLM")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[MT-BCR11-BLM](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "MT-BCR17-BL")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[MT-BCR17-BL](`r hyperlink`)

## BLM Nevada

### BLM in Nevada BCR 9
```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "NV-BCR9 BLM")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[NV-BCR9 BLM](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "NV-BCR9-BM")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[NV-BCR9-BM](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "NV-BCR9-CC")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[NV-BCR9-CC](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "NV-BCR9-EK")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[NV-BCR9-EK](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "NV-BCR9-EY")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[NV-BCR9-EY](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "NV-BCR9-NC")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[NV-BCR9-NC](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "NV-BCR9-SN")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[NV-BCR9-SN](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "NV-BCR9-WI")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[NV-BCR9-WI](`r hyperlink`)

## BLM Oregon

### BLM in Oregon BCR 9
```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "OR-BCR9 BLM")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[OR-BCR9 BLM](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "OR-BCR9-BU")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[OR-BCR9-BU](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "OR-BCR9-LA")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[OR-BCR9-LA](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "OR-BCR9-PR")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[OR-BCR9-PR](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "OR-BCR9-VA")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[OR-BCR9-VA](`r hyperlink`)

### BLM in Oregon BCR 10
```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "OR-BCR10 BLM")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[OR-BCR10 BLM](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "OR-BCR10-BU")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[OR-BCR10-BU](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "OR-BCR10-PR")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[OR-BCR10-PR](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "OR-BCR10-VA")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[OR-BCR10-VA](`r hyperlink`)

## BLM North Dakota
```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "ND-BCR17-BM")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[ND-BCR17-BM](`r hyperlink`)

## BLM South Dakota
```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "SD-BCR17-BM")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[SD-BCR17-BM](`r hyperlink`)

## BLM Utah
```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "UT-BLM")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[UT-BLM](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "UT-BCR9 BLM")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[UT-BCR9 BLM](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "UT-BCR10 BLM")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[UT-BCR10 BLM](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "UT-BCR16 BLM")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[UT-BCR16 BLM](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "UT-BLM - Cedar City Field Office")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[UT-BLM - Cedar City Field Office](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "UT-BLM - Fillmore Field Office")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[UT-BLM - Fillmore Field Office](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "UT-BCR16-KA")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[UT-BCR16-KA](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "UT-BCR16-MO")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[UT-BCR16-MO](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "UT-BCR16-MN")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[UT-BCR16-MN](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "UT-BCR16-PR")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[UT-BCR16-PR](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "UT-BLM - Richfield Field Office")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[UT-BLM - Richfield Field Office](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "UT-BLM - Saint George Field Office")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[UT-BLM - Saint George Field Office](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "UT-BLM - Salt Lake Field Office")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[UT-BLM - Salt Lake Field Office](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "UT-BLM - Vernal Field Office")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[UT-BLM - Vernal Field Office](`r hyperlink`)

## BLM Wyoming
```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "WY-BLM")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[WY-BLM](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "WY-BCR16-BL")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[WY-BCR16-BL](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "WY-BCR18-BL")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[WY-BCR18-BL](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "WY-BLM-Buffalo")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[WY-BLM-Buffalo](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "WY-BLM-Casper")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[WY-BLM-Casper](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "WY-BCR10-CO")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[WY-BCR10-CO](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "WY-BCR10-KE")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[WY-BCR10-KE](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "WY-BCR10-LA")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[WY-BCR10-LA](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "WY-BCR17-NE")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[WY-BCR17-NE](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "WY-BCR10-PI")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[WY-BCR10-PI](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "WY-BCR10-RA")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[WY-BCR10-RA](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "WY-BCR10-RO")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[WY-BCR10-RO](`r hyperlink`)


```{r, echo = FALSE, message = FALSE}

x <- which(data$stratum == "WY-BCR10-WO")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
hyperlink <- data[x, "hyperlink"]

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density and occupancy results and species counts within {name} across all years of the project, follow the web link below. Hit “Ok” on the Rocky Mountain Avian Data Center Disclaimer and hit the “Run Query” button highlighted in red located near the top of the page (the map will zoom to the area of interest). To view occupancy, density, or species counts results, click on the respective tab in the upper left above the map.")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

`r p5`

[WY-BCR10-WO](`r hyperlink`)

